Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-04-15 publication_materials/ms_rbc.tex
migration stash

\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{enumerate}
\usepackage{varwidth}
\usepackage{float}
\usepackage{nonfloat}
% \usepackage{afterpage}
\usepackage[usenames, dvipsnames]{color}
\newcommand{\note}[1]{\noindent \textbf{\textit{\textcolor{Red}{#1}}}}

@@

For various $Ra$ and fixed $Pr = 1$, we seek symmetric marginally-stable thermal equilibria (MSTE), thereby satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). 
We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:model} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebyshev polynomial basis. 
The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $Ra$ admit increasingly small-scale features. 
We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to compute $\langle w' T' \rangle_x$.

@@

\section{Properties of Thermally Equilibrated States}\label{sec:properties}
MSTE are fixed points of the quasilinear form derived in section \ref{sec:model}, differing from ECS in that ECS are fixed points of the full nonlinear problem (\ref{EQ:motion1})--(\ref{EQ:motion3}). 
Such definitions are not mutually exclusive, but in general we can assume that MSTE and ECS are not steady with respect to their counterparts' problems.
For this investigation, we calculate solutions for $Ra$ in the range $10^5 - 10^9$. 
Their mean temperatures $\bar{T}$ are symmetric about $z = 0$ by construction.

@@

The Nusselt number, which measures convective performance, is given by
\begin{equation}
  \Nu = 1 + \frac{A^2}{\mathcal{P}} \langle w'T' \rangle_x.
\end{equation}
There is no general consensus surrounding the scaling behavior of $\Nu$ for high $Ra$ systems, which are of particular importance in astrophysical systems. In Figure \ref{fig:nu_vs_ra} we report $\Nu$ for MSTE, ``steady rolls" ECS \cite{Wen}, and DNS \cite{Scheel_2016, Johnston}. 
All states obey $\Nu \sim Ra^{\beta}$ with classical scaling $\beta = 1/3$ in the ECS and MSTE. 
\cite{Wen} hypothesized that $\Nu$ of ECS which admit classical Malkus scaling must always exceed $\Nu$ of turbulent convection.
If we generalize this notion to include quasilinear equilibria, our findings agree; MSTE have larger $\Nu$ than 2D and 3D DNS.
This might be due to the chaotic transitions, among the unstable periodic orbits outlined by \cite{Yalniz, Cvitanovic}, inhibiting heat flux. 
We might also anticipate the existence of similar equilibria, having smaller $\Nu$ and occupying complementary nodes in the Markov chain whose long-term behavior agrees with DNS.

\section{Simulations with Thermally Equilibrated Initial Conditions}
This investigation is partially motivated by the prospect of decreasing DNS times by employing MSTE initial conditions. 
Conventionally, (\ref{EQ:motion1})--(\ref{EQ:motion3}) are solved via DNS with the linear initial conditions
\begin{align}
    T(x, z)\big|_{t=0} &= 0.5 - z \\
    \mathbf{u}(x, z)\big|_{t=0} &= \mathbf{0} \\
    p(x, z)\big|_{t=0} &= 0.
\end{align}
$t$ in this section now refers to the simulation time as opposed to the thermal equilibration time parameter used previously. 
We define the MSTE initial conditions
\begin{align}
    T(x, z)\big|_{t=0} &= \bar{T}(z) + \sqrt{2} \sum_{n=1}^N  A_n \text{ Re} \Big[ \theta_n(z) e^{ik_{x_n}x} \Big] \nonumber \\
    \mathbf{u}(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
    p(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[P_n (z) e^{ik_{x_n}x}\Big]
\end{align}
Where $\theta_n(z), U_n(z), W_n(z), P_n(z); \, A_n; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber at the $n$th marginal mode respectively. 
The $\sqrt{2}$ factor is necessary for eigenfunction normalization.

@@

% \begin{figure}
%     \centering
%     \includegraphics[width=3.4in]{sim_eq_nu.png}
%     \caption{Nusselt numbers of simulations performed at $Ra \, = \, 10^8$ with conventional initial conditions (red) and marginally-stable thermally-equilibrated initial conditions (blue). Simulations launched with thermally-equilibrated states do not undergo a convective-transient period because the characteristic plume structure exists on initialization. This is illustrated by the $Nu$ spike at $t \sim 15$ in the convectional simulation.}
%     \label{fig:nu_sim}
% \end{figure}
The average kinetic energy MSTE is significantly larger than the statistical steady state, as shown Figure \ref{fig:ke_sim}. 
This is postpones kinetic relaxation because the large-scale flows decay on a viscous time-scale
\begin{equation}
    t_{\nu} \sim \sqrt{\frac{Ra}{Pr}}. \nonumber
\end{equation}
Consequently, MSTE initial conditions do not reduce the simulation time required to achieve a statistically steady state -- instead they increase it considerably. This suggests the MSTE background state perspective is partially flawed, as an appropriate background state would approximate $\langle|\mathbf{u}|^2 \rangle_{\mathcal{D}}$ with more fidelity.
% \begin{figure}
%     \centering
%     \includegraphics[width=3.4in]{sim_eq_ke.png}
%     \caption{Average kinetic energies of the same simulations performed in Figure \ref{fig:nu_sim} ($Ra = 10^8$). The combination of eigenfunctions which give thermal equilibrium have significantly more kinetic energy than the statistically steady state. Kinetic equilibrium is achieved according to the viscous timescale $t_{\nu} \sim Pr Ra^{-1/2}$.}
%     \label{fig:ke_sim}
% \end{figure}
\begin{figure}
    \begin{minipage}{3.4in}
        \centering
        \includegraphics[width=3.4in]{sim_eq_nu.png}
        \caption{Nusselt numbers of simulations performed at $Ra = 10^8$ with the conventional initial conditions (black) and MSTE initial conditions (blue). 
        MSTE simulations do not undergo a convective-transient period because the characteristic large-scale convective cell structure exists on initialization.}
        \label{fig:nu_sim}
    \end{minipage}
\end{figure}

\begin{figure}
    \begin{minipage}{3.4in}
        \centering
        \includegraphics[width=3.4in]{sim_eq_ke.png}
        \caption{Average kinetic energies are reported for the simulations performed in Figure \ref{fig:nu_sim} at $Ra = 10^8$. 
        The combination of eigenfunctions associated with MSTE have significantly more kinetic energy than the statistically steady state. 
        Kinetic equilibrium is achieved according to the viscous timescale $t_{\nu} \sim \sqrt{Ra / Pr}$.}
        \label{fig:ke_sim}
    \end{minipage}
\end{figure}

@@

% Simulations performed with MSTE initial conditions do not undergo an initial convective transient period,

As previously noted, solving the EVP for statistically steady DNS data yields positive eigenvalues; the system is in a perpetual state of instability. 
Unstable modes tend to stabilize the system rapidly, creating a negative feedback loop whose average state is linearly unstable. 
We might curtail the disagreement between MSTE and DNS by loosening our marginal-stability criterion. 
Should the time-scales not be entirely separate, we might anticipate the long-term persistance of moderately unstable modes. 
This perpetual instability cannot be described by our model independently (we do not know, a priori, how unstable such modes are) but it might prove fruitful to investigate moderately unstable thermal equilibria (MUTE). 
More precisely, instead of traversing the manifold of marginally-stable states toward MSTE, we could consider the manifold of states whose maximum eigenvalue(s) $\omega_{\rm{max}}$ agree with some other stability constraint. 
Note that under this definition, 2-dimensional ECS are themselves MUTE, because they are thermally-equilibrated and generally unstable, though they need not satisfy the quasilinear form.

@@

>>>>

\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{longtable}
\usepackage{gensymb}
\usepackage{enumerate}
\usepackage{varwidth}
\usepackage{float}
\usepackage{nonfloat}
% \usepackage{multicol}
% \usepackage{afterpage}
\usepackage[usenames, dvipsnames]{color}
\newcommand{\note}[1]{\noindent \textbf{\textit{\textcolor{Red}{#1}}}}

@@

For various $Ra$ and fixed $Pr = 1$, we seek marginally-stable thermal equilibria (MSTE) satisfying $\frac{\partial \bar{T}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). 
We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:model} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebyshev polynomial basis. 
The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large $Ra$ admit increasingly small-scale features. 
We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to compute $\langle w' T' \rangle_x$.

@@

\section{Properties of Thermally Equilibrated States}\label{sec:properties}
MSTE are fixed points of the quasilinear form derived in section \ref{sec:model}, differing from ECS in that ECS are fixed points of the full nonlinear problem (\ref{EQ:motion1})--(\ref{EQ:motion3}). 
Such definitions are not mutually exclusive, but in general we can assume that MSTE and ECS are not steady with respect to their counterparts' problems.
We compute symmetric MSTE for $Ra$ in the range $10^5 - 10^9$.

@@

The Nusselt number, which measures convective performance, reduces to
\begin{equation*}
    \Nu = \frac{\langle A^2 \langle w'T' \rangle_x - \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}{\langle- \mathcal{P}\frac{\partial \bar{T}}{\partial z} \rangle_z}.
\end{equation*}
There is no general consensus surrounding the scaling behavior of $\Nu$ for high $Ra$ systems, which are of particular importance in astrophysical systems. In Figure \ref{fig:nu_vs_ra} we report $\Nu$ for MSTE, ``steady rolls" ECS \cite{Wen}, and DNS \cite{Scheel_2016, Johnston}. 
All states obey $\Nu \sim Ra^{\beta}$ with classical scaling $\beta = 1/3$ in the ECS and MSTE. 
\cite{Wen} hypothesized that $\Nu$ of ECS which admit classical Malkus scaling must always exceed $\Nu$ of turbulent convection.
If we generalize this notion to include quasilinear equilibria, our findings agree; MSTE have larger $\Nu$ than 2D and 3D DNS.
This might be due to the chaotic transitions, among the unstable periodic orbits outlined by \cite{Yalniz, Cvitanovic}, inhibiting heat flux. 
We might also anticipate the existence of similar equilibria, having smaller $\Nu$ and occupying complementary nodes in the Markov chain whose long-term behavior agrees with DNS.

\section{Simulations with Thermally Equilibrated Initial Conditions}
This investigation is partially motivated by the prospect of decreasing DNS times by employing MSTE initial conditions. 
Conventionally, (\ref{EQ:motion1})--(\ref{EQ:motion3}) are solved via DNS with the linear initial conditions
\begin{align}
    T(x, z)\big|_{t=0} &= 0.5 - z \nonumber \\
    \mathbf{u}(x, z)\big|_{t=0} &= \mathbf{0} \nonumber \\
    p(x, z)\big|_{t=0} &= 0 \label{EQ:linear_ic}.
\end{align}
$t$ in this section now refers to the simulation time as opposed to the thermal equilibration time parameter used previously. 
We define the MSTE initial conditions
\begin{align}
    T(x, z)\big|_{t=0} &= \bar{T}(z) + \sqrt{2} \sum_{n=1}^N  A_n \text{ Re} \Big[ \theta_n(z) e^{ik_{x_n}x} \Big] \nonumber \\
    \mathbf{u}(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[\Big( U_n (z) \hat{x} + W_n(z) \hat{z} \Big) e^{ik_{x_n}x} \Big] \nonumber\\
    p(x, z)\big|_{t=0} &= \sqrt{2} \sum_{n=1}^N A_n \text{ Re} \Big[P_n (z) e^{ik_{x_n}x}\Big] \label{EQ:mste_ic}
\end{align}
where $\theta_n(z), U_n(z), W_n(z), P_n(z); \, A_n; $ and $k_{x_n}$ refer to the complex eigenfunctions, amplitude, and wavenumber at the $n$th marginal mode respectively. 
The $\sqrt{2}$ factor is necessary for eigenfunction normalization.

\begin{figure}
    \begin{minipage}{3.4in}
        \centering
        \includegraphics[width=3.4in]{sim_eq_nu.png}
        \caption{Nusselt numbers of simulations performed at $Ra = 10^8$ with the conventional initial conditions (black) and MSTE initial conditions (blue). 
        MSTE simulations do not undergo a convective-transient period because the characteristic large-scale convective cell structure exists on initialization.}
        \label{fig:nu_sim}
    \end{minipage}
\end{figure}

@@

\begin{figure}
    \begin{minipage}{3.4in}
        \centering
        \includegraphics[width=3.4in]{sim_eq_ke.png}
        \caption{Average kinetic energies are reported for the simulations performed in Figure \ref{fig:nu_sim} at $Ra = 10^8$. 
        The combination of eigenfunctions associated with MSTE have significantly more kinetic energy than the statistically-steady state. 
        Kinetic equilibrium is achieved according to the viscous time-scale $t_{\nu} \sim \sqrt{Ra / Pr}$.}
        \label{fig:ke_sim}
    \end{minipage}
\end{figure}

The average kinetic energies of MSTE are significantly larger than those associated with the statistically-steady state, as shown Figure \ref{fig:ke_sim}. 
This is postpones kinetic relaxation because the large-scale flows decay on a viscous time-scale

\begin{equation}
    t_{\nu} \sim \sqrt{\frac{Ra}{Pr}}. \nonumber
\end{equation}

Consequently, MSTE initial conditions do not reduce the simulation time required to achieve a statistically-steady state -- instead they increase it considerably. 
This suggests the MSTE background state perspective is partially flawed, as an appropriate background state would approximate $\langle|\mathbf{u}|^2 \rangle_{\mathcal{D}}$ with more fidelity.

@@

Simulations performed with MSTE initial conditions (\ref{EQ:mste_ic}) do not undergo an early convective transient period, but have faster flows and greater $\Nu$ when compared with DNS. 
From a dynamical systems perspective, unstable orbits depart from MSTE and approach the global attractor (the compact manifold of states whose weighted-average agrees with experiments) on a viscous time-scale. This requires more $CPU-hr$ to achieve relaxation as compared to the conventional linear initial condition (\ref{EQ:linear_ic}).

As previously noted, solving the EVP for statistically-steady DNS data yields positive eigenvalues; the system is in a perpetual state of instability. 
Unstable modes tend to stabilize the system rapidly, creating a negative feedback loop whose average state is linearly unstable. 
We might curtail the disagreement between MSTE and DNS by loosening our marginal-stability criterion. 
Should the time-scales not be entirely separate, we might anticipate the long-term persistance of moderately unstable modes. 
Such an instability cannot be described by our model independently (we do not know, a priori, \textit{how unstable} MUTE should be) but it might prove fruitful to investigate moderately unstable thermal equilibria (MUTE). 
More precisely, instead of traversing the manifold of marginally-stable states toward MSTE, we could consider the manifold of states whose maximum eigenvalue(s) $\omega_{\rm{max}}$ agree with some other stability constraint. 
Note that under this definition, 2-dimensional ECS are themselves MUTE, because they are thermally-equilibrated and generally unstable, though they need not satisfy the quasilinear form.

@@

% \begin{multicols}{1}
\subsection{MSTE Metrics}
\begin{longtable*}{cccccc}
    %\begin{tabular}{cccccc}
    %\hline
    %\begin{longtable}[c]{@{}*{6}{>{\arraybackslash}p{0.15\linewidth}}@{}}
    \quad\quad\quad Ra	\quad\quad\quad	&	\quad\quad\quad		Pr	\quad\quad\quad		&	\quad\quad\quad		$k=2\pi/\Gamma$	\quad\quad\quad		&	\quad\quad\quad		$N_x \times N_z$	\quad\quad\quad		&	\quad\quad\quad		Nu	\quad\quad\quad		&	\quad\quad\quad		Re	\quad\quad\quad\\
    %\hline
    $10^{13/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.056590	&	1.617336\\
    $1.9\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.145807	&	2.682155\\
    $2\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.212037	&	3.317190\\
    $2.25\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.355410	&	4.550975\\
    $2.5\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.474455	&	5.537770\\
    $2.75\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.575599	&	6.391812\\
    $3\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.663162	&	7.159844\\
    $10^{14/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.714193	&	7.624400\\
    $3.5\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.808754	&	8.526064\\
    $4\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	1.926775	&	9.740578\\
    $4.5\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	2.025985	&	10.85141\\
    $5\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	2.111714	&	11.88534\\
    $10^{15/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	2.204811	&	13.09152\\
    $8\times10^3$	&	1	&	$\pi$	&	128 $\times$ 65	&	2.476330	&	17.05494\\
    $10^4$	&	1	&	$\pi$	&	128 $\times$ 65	&	2.648664	&	20.07400\\
    $10^{17/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	3.122843	&	29.50047\\
    $10^{18/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	3.665041	&	42.29585\\
    $10^{19/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	4.287042	&	59.56858\\
    $10^{5}$	&	1	&	$\pi$	&	128 $\times$ 65	&	4.994322	&	82.84462\\
    $10^{21/4}$	&	1	&	$\pi$	&	128 $\times$ 65	&	5.795869	&	114.2355\\
    $10^{22/4}$	&	1	&	$\pi$	&	128 $\times$ 97	&	6.703915	&	156.5252\\
    $10^{23/4}$	&	1	&	$\pi$	&	128 $\times$ 97	&	7.732236	&	213.4031\\
    $10^{6}$	&	1	&	$\pi$	&	128 $\times$ 97	&	8.896615	&	289.7982\\
    $10^{25/4}$	&	1	&	$\pi$	&	256 $\times$ 97	&	10.21546	&	392.2837\\
    $10^{26/4}$	&	1	&	$\pi$	&	256 $\times$ 129	&	11.71065	&	529.6372\\
    $10^{27/4}$	&	1	&	$\pi$	&	256 $\times$ 129	&	13.40898	&	713.6005\\
    $10^{7}$	&	1	&	$\pi$	&	512 $\times$ 129	&	15.34493	&	959.9367\\
    $1.35\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 129	&	16.46456	&	1119.932\\
    $1.5\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 129	&	16.87881	&	1182.172\\
    $1.6\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.13944	&	1222.005\\
    $1.65\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.26636	&	1241.484\\
    $1.7\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.39216	&	1260.709\\
    $1.736\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.48282	&	1274.414\\
    $1.76\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.54351	&	1283.493\\
    $10^{29/4}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.58987	&	1290.377\\
    $1.786\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.60946	&	1293.277\\
    $1.8\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.64500	&	1298.522\\
    $1.85\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.77160	&	1317.122\\
    $1.9\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	17.89693	&	1335.501\\
    $1.95\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	18.02044	&	1353.657\\
    $2\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	18.14193	&	1371.593\\
    $2.4\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	19.04221	&	1507.890\\
    $2.8\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	19.83413	&	1633.418\\
    $10^{30/4}$	&	1	&	$\pi$	&	512 $\times$ 193	&	20.47798	&	1739.647\\
    $4.5\times10^{7}$	&	1	&	$\pi$	&	512 $\times$ 193	&	22.44036	&	2087.182\\
    $10^{31/4}$	&	1	&	$\pi$	&	512 $\times$ 193	&	23.76002	&	2340.822\\
    $10^{8}$	&	1	&	$\pi$	&	768 $\times$ 257	&	27.50669	&	3144.931\\
    $10^{33/4}$	&	1	&	$\pi$	&	768 $\times$ 257	&	31.81154	&	4220.616\\
    $2.15\times10^{8}$	&	1	&	$\pi$	&	768 $\times$ 257	&	33.36657	&	4649.541\\
    $10^{34/4}$	&	1	&	$\pi$	&	768 $\times$ 257	&	36.75427	&	5658.648\\
    $4.64\times10^{8}$	&	1	&	$\pi$	&	896 $\times$ 321	&	40.44652	&	6875.704\\
    $10^{35/4}$	&	1	&	$\pi$	&	896 $\times$ 321	&	42.42917	&	7580.057\\
    $10^{9}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	48.94284	&	10145.79\\
    $10^{37/4}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	56.42926	&	13571.10\\
    $2.15\times10^{9}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	59.13988	&	14935.81\\
    $2.5\times10^{9}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	61.38714	&	16116.94\\
    $10^{38/4}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	65.06338	&	18145.61\\
    $10^{153/16}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	67.42466	&	19511.79\\
    $4\times10^{9}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	68.96487	&	20429.24\\
    $4.64\times10^{9}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	71.58241	&	22019.93\\
    $10^{39/4}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	75.09725	&	24262.22\\
    $10^{10}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	86.68318	&	32430.06\\
    $10^{41/4}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	100.0909	&	43339.02\\
    $2\times10^{10}$	&	1	&	$\pi$	&	1024 $\times$ 321	&	103.0738	&	45995.60\\
    $2.15\times10^{10}$ &	1	&	$\pi$	&	1024 $\times$ 321	&	104.9517	&	47705.08\vspace{0.1in}\\
    %\hline
    %  \end{tabular}
    \caption*{Table S1: Details for numerical solutions with $\Pran=1$ and $\Gamma=2$.  $N_x$ and $N_z$ represent the numbers of Fourier and Chebyshev modes, respectively.}
    {\label{tab:Gamma2}}
    \end{longtable*}
% \end{multicols}
